Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)

### 2014-03-06 MHCpaper/MHCsupp.tex
changed ko labels

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}[table]
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figureautorefname}{Supplementary Figure}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
%\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^{\mathrm{b}-/-}$}
\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 S#2}}
\captionsetup{labelformat=supp}

@@

\begin{figure}[p]
\begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l@{\hspace{0.05\linewidth}}l}
      \item\label{fig:seial_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_sim}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.125\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate.svg}}
      \\[1.5cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{multistate_med_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{binary_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{multistate_lin_learnS.eps}}
      \\[5.5cm]
      \item\label{fig:pooled_sim}
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate_nonuni.svg}}
      \\[2cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{cascade_long_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{nonuni_learnS.eps}}
  \end{tabular}

@@

    \cline{1-10}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.11 & 0.89 & 5  & 100  &\label{tr:serial_fit} \\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002 & 1.5  & 200  &\label{tr:cascade_fit} \\
    Non-uni. & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 5  & 500  &\label{tr:nonuni_fit} \\
    \cline{1-10}
  \end{tabularn}}
 \end{myenuma}
 \end{center}
  \caption[Learning curves for models after parameter fitting]{Learning curves restricted to gain-increase training, for (\ref{fig:serial_fit}) the serial model, (\ref{fig:cascade_fit}) the cascade model, and (\ref{fig:nonuni_fit}) the non-uniform multistate model.
  (\ref{tab:fit}) Parameters used to reproduce detailed experimental results. For the serial model, the parameter listed is the transition probability between adjacent states. For the cascade and non-uniform multistate models, the parameter is the ratio of adjacent transition probabilities.}\label{fig:fit}
\end{figure}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
\documentclass[10pt]{article}
%\usepackage[printfigures]{figcaps}
%\usepackage[nolists,nomarkers]{endfloat}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\hypersetup{colorlinks,linkcolor=blue,citecolor=teal,urlcolor=teal}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}[table]
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
\renewcommand{\figureautorefname}{Supplementary Figure}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\I}{\mathbf{I}}
%vec of ones
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%other symbols
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{K$^\mathrm{b}$D$^\mathrm{b}$-/-}}}
\newcommand{\KO}{K$^\mathrm{b}$D$^{\mathrm{b}-/-}$}
%\newcommand{\ko}{_{\text{MHC}}}
%\newcommand{\KO}{MHC}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Understanding both enhanced and impaired learning with enhanced plasticity: a saturation hypothesis (supplementary material)}
%
%% Author List:
%%
%\author{An Author$^a$, Another Author$^b$ and Yet Another Author$^c$\\
%%
%\small{\emph{$^a$ Address 1}}\\
%\small{\emph{$^b$ Address 2}}\\
%\small{\emph{$^c$ Address 3}}\\
%}
\date{}
\DeclareCaptionLabelFormat{supp}{\textbf{#1 S#2}}
\captionsetup{labelformat=supp}

@@

\begin{figure}[p]
\begin{myenuma}
  \begin{tabular}{l@{\hspace{0.05\linewidth}}l@{\hspace{0.05\linewidth}}l}
      \item\label{fig:seial_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{serial.svg}}
      &
      \item\label{fig:binary_sim}
      \hspace{0.05\linewidth}\aligntop{\includegraphics[width=0.125\linewidth]{binary.svg}}
      &
      \item\label{fig:multistate_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate.svg}}
      \\[1.5cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{serial_med_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{binary_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{multistate_lin_learnS.eps}}
      \\[5.5cm]
      \item\label{fig:pooled_sim}
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly.svg}}
      &
      \item\label{fig:cascade_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{cascade.svg}}
      &
      \item\label{fig:nonuni_sim}
      \aligntop{\includegraphics[width=0.25\linewidth]{multistate_nonuni.svg}}
      \\[2cm]
      \aligntop{\includegraphics[width=0.3\linewidth]{pooled_deponly_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{cascade_long_learnS.eps}}
      &
      \aligntop{\includegraphics[width=0.3\linewidth]{nonuni_learnS.eps}}
  \end{tabular}

@@

    \cline{1-10}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.89 & 0.11 & 5  & 100  &\label{tr:serial_fit} \\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002 & 1.5  & 200  &\label{tr:cascade_fit} \\
    Non-uni. & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 5  & 500  &\label{tr:nonuni_fit} \\
    \cline{1-10}
  \end{tabularn}}
 \end{myenuma}
 \end{center}
  \caption[Learning curves for models after parameter fitting]{Learning curves restricted to gain-increase training, for (\ref{fig:serial_fit}) the serial model, (\ref{fig:cascade_fit}) the cascade model, and (\ref{fig:nonuni_fit}) the non-uniform multistate model.
  (\ref{tab:fit}) Parameters used to reproduce detailed experimental results. For the serial model, the parameter listed is the transition probability between adjacent states. For the cascade and non-uniform multistate models, the parameter is the ratio of adjacent transition probabilities.}\label{fig:fit}
\end{figure}
